My title

### 2024-04-14 paper/paper.qmd
Add completed model section to paper

#Read in model
beyonce_pois <- readRDS(file = here::here("models/beyonce_pois.rds"))
beyonce_nbinom <- readRDS(file = here::here("models/beyonce_nbinom.rds"))

```

@@

In @fig-posteriorvsprior we compare the posterior with the prior. @fig-posteriorvsprior-1 suggests that there is an issue with the default prior we specified for $\alpha$. Our re-specified model in @fig-posteriorvsprior-2 shows that it does a better job of fitting the data.

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| fig-cap: "Comparing the posterior with the prior"
#| #| fig-subcap: ["Default priors", "Re-specified priors"]
#| layout-ncol: 2

>>>>

#Read in model
beyonce_pois <- readRDS(file = here::here("models/beyonce_pois.rds"))
beyonce_nbinom <- readRDS(file = here::here("models/beyonce_nbinom.rds"))
beyonce_nbinom_default <- readRDS(file = here::here("models/beyonce_nbinom_default.rds"))
```

@@

We compare the posterior with the prior. @fig-posteriorvsprior-1 suggests that there is an issue with the default prior we specified for $\alpha$. Our re-specified model in @fig-posteriorvsprior-2 shows that it does a better job of fitting the data.

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-posteriorvsprior
#| fig-cap: "Comparing the posterior with the prior"
#| fig-subcap: ["Default priors", "Re-specified priors"]
#| layout-ncol: 2
